Manuscript

### 2025-03-05 Manuscript_MD_ScoreReLiability.qmd

As all phenomena in the collection fulfil the first condition, 50
phenomena have been catalogued where the effect is studied by comparing
the outcome across two separate groups. While the majority of designs
make use of some form of control-treatment manipulation, randomly
assigning participants to a condition (20 phenomena), some phenomena
discuss the effect of pre-existing differences, e.g. biological sex (2
phenomena). From the collection of 50 phenomena, 22 fulfil the second
condition, so that estimates of score reliability can be derived. For
these phenomena, the dependent variable used to construct the effect
size is measured by employing more than a single indicator. At the same
time, however, this implies that the remaining 28 phenomena did not make
use of more than a single indicator to measure the dependent variable.
Therefore, for the majority of phenomena it is not possible to assess in
how far measurement quality is sufficiently high in terms of e.g.
internal consistency or low random error variance.

From the 22 phenomena that employed more than a single indicator, 19
made use of Likert-style items, where respondents would indicate their
agreement to some kind of statement. The scale-length varied from 3 to
10-points. The items measuring the remaining 3 phenomena were coded
dichotomously, as responses were right or wrong (2 cases), or expressed
agreement vs disagreement dichotomously (1 case). Subsequently, those
phenomena need to be identified where the meta-analytic mean effect size
is statistically significant different from zero. This will be done as a
first step of this manuscript’s analysis procedure. Detailed information
concerning the different phenomena and how they were measured can be
found at \[osf-link\], while a brief summary can be found in Table A.

>>>>

As all phenomena in the collection fulfil the first condition, 50
phenomena have been catalogued where the effect is studied by comparing
the outcome across two separate groups. From the collection of 50
phenomena, 22 fulfil the second condition, so that estimates of score
reliability can be derived. For the 22 phenomena, the dependent variable
used to construct the effect size is measured by employing more than a
single indicator. At the same time, however, this implies that the
remaining 28 phenomena did not make use of more than a single indicator
to measure the dependent variable. Therefore, for the majority of
phenomena it is not possible to assess in how far measurement quality is
sufficiently high in terms of e.g. internal consistency or low random
error variance.

From the 22 phenomena that employed more than a single indicator, 19
made use of Likert-style items, where respondents would indicate their
agreement to some kind of statement. The scale-length varied from 3 to
10-points. The items measuring the remaining 3 phenomena were coded
dichotomously, as responses were right or wrong (2 cases), or expressed
